% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Carson Page}
\newcommand{\CVTitle}{Carson Page's Resume for Collins}
\newcommand{\CVNote}{Resume compiled on {\today} for Collins}
\newcommand{\CVWebpage}{https://carson.page/}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
7301 Alma Dr. Apt 1612, Plano, Texas 75025
\par
\href{mailto:me@carson.page}
{me@carson.page}
\,\SubBulletSymbol\,
+1\,(512)\,630-6908
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{https://utdallas.edu/}
{\textbf{The University of Texas at Dallas}},
Richardson, Texas
\hfill
\DatestampYMD{2017}{08}{19} -- Present
\Gap
\BulletItem
B.S. in
\href{https://cs.utdallas.edu/}
{Computer Science} (Expected \DatestampYM{2021}{5})

\BigGap
\Entry
\textbf{Hutto High School}
Hutto, Texas
\hfill
\DatestampYM{2017}{05}
\Gap
\BulletItem Diploma

%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Work Experience}
{Work Experience}
{PDF:WorkExpiriance}

% \Entry
% \href{https://www.collinsaerospace.com/}{\textbf{Collins Aerospace}},
% Richardson, Texas
% \hfill
% \DatestampYM{2020}{01} -- Present
% \Gap
% Software Engineer, Co-Op
% HFGCS, Mission Software Systems
% \begin{Detail}
% \BulletItem
% Developed tools and systems for testing and intergration of HFGCS software.
% \BulletItem
% Partipated in critical project to update 
% \end{Detail}

\BigGap
\Entry
\href{https://byterealm.com/}{\textbf{Byte Realm Solutions LLC}},
Dallas, Texas
\hfill
% \DatestampYM{2018}{02} -- \DatestampYM{2019}{12}
\DatestampYM{2018}{02} -- Present
\Gap
Software Developer, Self-Employed
\begin{Detail}
\BulletItem
Provide software consulting and design services.
\BulletItem
Develop and maintain web solutions for customers.
\BulletItem
Maintain infrastructure and IT resources in both cloud and on-prem enviroments.
\BulletItem
Assist on IoT development and deployment project.
\BulletItem
Continued work for X-Microwave on a contractual basis,
assuming many previous responsibilities.
\end{Detail}

\BigGap
\Entry
\href{https://keysight.com/}{\textbf{Keysight Technologies}},
Dallas, Texas (Remote)
\hfill
\DatestampYM{2018}{02} -- \DatestampYM{2018}{10}
\Gap
Software Developer
\begin{Detail}
\BulletItem
Internship with Keysight Eagleware team, responsible for
Genesys, SystemVue, and other EDA products.
\BulletItem
Developed new device library management system for Genesys, including
automatic installer and update functionality.
\BulletItem
Improved vendor tooling, enabling easier automation of library generation.
\end{Detail}

\BigGap
\Entry
\href{https://www.xmicrowave.com/}{\textbf{X-Microwave LLC}},
Round Rock, Texas
\hfill
\DatestampYM{2014}{04} -- \DatestampYM{2017}{12}
\Gap
Software Developer
\begin{Detail}
\BulletItem
Designed and maintained the first web-based non-linear RF / Microwave simulator.
\BulletItem
Maintained on-site Active Directory and group policies.
\BulletItem
Managed company network security, including firewall rules and monitoring.
\BulletItem
Developed online web applications, deployed on Amazon Web Services for external
and internal use.
\BulletItem
Maintained company website written with Wordpress / PHP.
\end{Detail}

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

%% Woe is me

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\Gap
\BulletItem
Academic Excellence Scholarship
\hfill
\DatestampYMD{2017}{08}{19}
\newline
The University of Texas of Dallas
\begin{Detail}
\Item
Partial-tuition scholarship for undergraduate studies.
\end{Detail}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Activities \& Organizations}
{Activities \& Organizations}
{PDF:ActivitiesOrganizations}

\Entry
\textbf{Neighborhood WISP Co-Op}
\newline
Georgetown, Texas

System Administrator
\hfill
\DatestampY{2015} -- \DatestampY{2017}
\begin{Detail}
\BulletItem
Helped design and maintain a small wireless ISP for the
aviation community I lived in on a volunteer basis.
\BulletItem
Operated multiple 5GHz UNII band PtP and PtMP links, oversaw network
design and upgrades.
\end{Detail}
% Manual page break.
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\Section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
Programming:
C,
C++,
C\#,
Rust.

\Gap
\BulletItem
Scripting: Bash, JavaScript, PHP, Python, SQL, Pg/SQL.

\BulletItem
Hardware: Verilog / SystemVerilog,
VHDL.

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
% {\TeX}, {\LaTeX}, {\XeLaTeX},
% MATLAB,
% Mathematica,
% Maple,
% R,
% Tableau,
% Adobe Photoshop,
% Adobe Illustrator,
% Microsoft Word,
% Microsoft Excel,
% Microsoft PowerPoint.
Active Directory,
Amazon Web Services,
CI/CD Pipelines,
COM / WinApi,
Embedded Design,
FPGA Design,
FreeRTOS,
Git,
Linux,
PostgreSQL,
Relational Database Design,
Shell Scripting,
WPF.


%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Interests}
{Interests}
{PDF:Interests}

\Entry
\href{https://wireless2.fcc.gov/UlsApp/UlsSearch/license.jsp?licKey=3209531}{Amateur Radio - General Class}
\newline
Digital Electronics

\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\BigGap
\UseNoteFont%
\null\hfill%
[\textit{\CVNote}]

\end{document}
